---
title: "report"
date: "4/25/2020"
output: 
  prettydoc::html_pretty:
    theme: cayman
params:
  box_plots: NA
  
---


## Using Parametrized RMD's for Custom Report Format

```{r include=FALSE}
library(rpart)
library(visNetwork)
library(DT)

if("prettydoc" %in% rownames(installed.packages()) == FALSE) {install.packages("prettydoc")}

knitr::opts_chunk$set(fig.align="center")
options(DT.options = list(autoWidth = TRUE, autoHeight = TRUE))
```

### Using Markdown to format the doc easily

# **MSstatsQC Framework Report**

## Including Plots {PCA, TREE, RULES}

We can also embed plots:

### Pair Plot
```{r, echo=FALSE}
require(plotly)
for (p in params$box_plots) {
  plot(p)
}

```

### 3D PCA
```{r, echo=FALSE}
# params$plotly_fig
```

### Tree
```{r, echo=FALSE}
# visTree(params$tree_plot, main = "Anomaly Classification Tree", width = "100%")
```

### Rule Table

```{r echo=FALSE}
# DT::datatable({params$rule_table}
#   ,escape = F
#   ,fillContainer = T
#   ,options = list(lengthMenu = c(25, 50, 100), pageLength = 25,scrollY = FALSE,
#                   rowCallback = DT::JS(sprintf('function(row, data) {
#                                           if (String(data[%s]).trim() == "Anomaly"  ){
#                                                   $("td", row).css("background", "#994141");
#                                                   $("td", row).css("color", "white");}}',toString(1)))
#   )
#   )

```

<code>MSstatsQC</code> is an open-source R package and Shiny web application for statistical monitoring of quality control (QC) samples produced by spectrometry-based proteomic experiments. <code>MSstatsQC</code> is available through <a href="www.msstats.org/msstatsqc">www.msstats.org/msstatsqc</a>.
